---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# basecamper

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of basecamper is to work with Basecamp Classic API to interact with Basecamp directly from R.

What you can do with this package:

 |Scope|Query|Post|Edit|Delete|Download|Vignette|
 |:--:|:--:|:--:|:--:|:--:|:--:|:--:|
 |Projects|`r emo::ji('check')`|||||`r emo::ji('check')`|
 |Messages|`r emo::ji('check')`|`r emo::ji('check')`|`r emo::ji('check')`|`r emo::ji('check')`||
 |Comments|`r emo::ji('check')`|`r emo::ji('check')`|`r emo::ji('check')`|`r emo::ji('check')`||`r emo::ji('check')`|
 |Attachments|`r emo::ji('check')`|`r emo::ji('check')`|||`r emo::ji('check')`|`r emo::ji('check')`|
 
## Installation

To use this package clone the repository and install locally

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(basecamper)
```

Set up the TOKEN and HOST

You can find your TOKEN by logging into Basecamp

  - Click on `My info` found in the top right corner of the website
  - At the bottom of this page you will see `Authentication tokens`, click on `Show your tokens`
  - Copy the `Token for feed readers or the Basecamp API`, this goes into the `BASECAMP_TOKEN` environment variable.

```{r,eval=FALSE}
Sys.setenv(BASECAMP_TOKEN = 'MYTOKEN')
Sys.setenv(BASECAMP_HOST  = 'https://metrumresearchgroup.basecamphq.com')
```


### Whoami

Lets just check that the token and host are set right and get back your account info

```{r}
basecamper::whoami()
```

