---
title: "Attachments"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Attachments}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(basecamper)
```

## Attachments

```{r}

MYPROJECT <- '8514810'

attachments <- basecamper::basecamp_attachments(MYPROJECT)
```

### Inspecting Attachments

Print method for attachment object lists the names of the files attached in the project

```{r}
print(attachments)
```

Summary method for an attachment object returns a tibble with information about the files: filename, when it was created, file size and the url to download it (which is most important)

```{r}
summary(attachments)
```

## Downloading Attachments

```{r}
attach_summary <- summary(attachments)

(file_url  <- attach_summary$url[3])

td <- tempdir()

basecamp_download(file_url,destdir = td)

```

### Downloaded file information

```{r}
list.files(td,pattern = '.zip$')

fs::as_fs_bytes(file.info(list.files(td,pattern = '.zip$',full.names = TRUE))[,'size'])
```

## Unzip Archives

`basecamper::unzip2` runs unzip from CLI which is more robust for files larger than `4gb` which are truncated by `utils::unzip`

```{r}

zipped_file <- list.files(td,pattern = '.zip$',full.names = TRUE)

basecamper::unzip2(directory = td,file = zipped_file)
```

### Unzipped files information

```{r}

zip_dir <- tools::file_path_sans_ext(list.files(td,pattern = '.zip$',full.names = TRUE))

unzipped_files <- fs::file_info(
  list.files(zip_dir,full.names = TRUE)
  )[,c('path','size')]

# clean up the path for printing
unzipped_files$path <- basename(unzipped_files$path)

unzipped_files

```
