---
title: "Creating and Querying Comments"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating and Querying Comments}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(basecamper)
```

```{r}
whoami()
```


```{r}
projs <- basecamp_projects()
```

```{r}

(projs_sum <- summary(projs))

```
 
```{r}
(proj_id <- projs_sum$id[grepl('TAK0208F',projs_sum$name)])
```
 
```{r}

proj_msgs <- basecamp_messages(scope = 'project',id = proj_id)

```
 
```{r}

(proj_msgs_sum <- summary(proj_msgs))

```
 
```{r}

(msg_id <- proj_msgs_sum$id[grepl('Project Log',proj_msgs_sum$title)])
  
```

## View a message contents

### Convert message from XML to an html file

```{r}
msg_file <- proj_msgs%>%
  message_to_html(index = 1) # default a tempfile
```

```{r, results='asis'}
cat(readLines(msg_file,warn = FALSE))
```

## Creating a Comment

```{r,eval = FALSE}
new_comment <- create_comment(scope = 'posts',id = msg_id)

```

### Write the body for the comment

The body can be in two forms

  - Regular text
  - HTML
    - You can write in Markdown and convert it to HTML
    - You can render a Rmarkdown with an `html_document` output to read in the content

```{r}
my_body <- 
'What happened in the meeting

1. We went over the 2.7.2 schedule and the following tables were highlighted

  - Tables: 3.k, 3.m
  - Figures: 3.d

2. Clarification of SoW

  - In the logistic regressions the relevant subjects are week 6 responders
  - Missing baseline covariate values will be imputed by the population median

3. Data assembly for response data in IV trial was discussed.

  - Verified that the data we have in the archive is what they have internally

4. Report structure

  - After internal discussions they have decided that two reports are needed
    - Submission: SC trial
    - Publication: SC + IV trials

5. Timelines

  - Exposure simulations ETA 10/18
  - Initial ER results 10/31

'

```
 
### Convert to HTML 
```{r}
my_body_html <- markdown::markdownToHTML(text = my_body,fragment.only = TRUE)
```

<details> 
<summary>HTML output (Click to open)</summary>
```{r,echo=FALSE,results='asis'}
cat(my_body_html)
```
</details> 

### Add the body to the new comment object

```{r,eval=FALSE}
new_comment%>%
  edit_body(my_body_html)

```
 
## Send the Comment to the Message Thread
 
```{r,eval=FALSE}
new_comment%>%
  basecamper::post_comment()
```
