---
title: "Projects"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Projects}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(basecamper)
```

## Retrieve all Projects

```{r}
projects <- basecamper::basecamp_projects()
```

## Inspecting Projects

### Print

The print method for the `projects` object will return a character vector with the project name with the company associated with it as the element name.

```{r}
projects
```

### Summary

Summary method for a `projects` object will return a `tibble` with `company` name associated with the project, with the `id` and `name` of the project.

```{r}
summary(projects)
```

## Retrieve all Projects

Choose a project

```{r}
(METRUM <- summary(projects)[[2,'id']])
```

```{r}
project <- basecamper::basecamp_project(METRUM)
```

## Inspecting a Project

### Print

Printing the `project` object will return basic meta information

```{r}
project
```

